NFC and burnout in teachers - A replication and extension study

### 2022-07-20 Manuscript/Manuscript.Rmd
added replication 'in a teacher sample'

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and student teachers [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor [@Strobel2017].
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
This can take the form of patients with higher NFC having lower intentions to consult their physician [@Latimer2007] or adults with higher NFC having higher intentions to consume high calorie beverages [@Gallivan2020] after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery [@Salanova2006].
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (*demands too high*), demands that are too low for one’s personal resources (*demands too low*), and a balanced fit of demands and resources (*demand-resource-fit*).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with *demands too high*, and positively associated with *demands too low* and *demand-resource-fit*.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with *demands too high* and negatively associated with *demand-resource-fit*.
However, we had no hypothesis regarding the association of *demands too low* and burnout, because even though *demands too low* is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.

@@

### Replication of Grass et al. (2018)
Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
*Reduced personal efficacy* was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
Following Grass et al. [-@Grass2018], bootstrapped confidence intervals with $N=2,000$ replicates <!-- add seed and RNG (likely "Mersenne-Twister" --> were computed to account for deviations from normality.
Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model ($CFI>.95$ indicates good fit, but $CFI>.90$ is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix ($SRMR<.08$ indicates fair fit, $SRMR<.05$ good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account ($RMSEA<.08$ indicates acceptable fit, $RMSEA<.05$ good fit, $RMSEA<.01$ excellent fit).

@@

```{r objective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}

  replic_table <-
    knitr::kable(replic_table,
        caption = "Results of the replication of Grass et al. (2018).",
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
    kableExtra::pack_rows("Total Effect", 11, 11) %>%
    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, \\beta = standardized regression coefficient, $CI$ = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

## Replication of Grass et al. (2018)

@@

```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized regression coefficients in the replication of Grass et al. (2018). * $p<.05$, ** $p<.01$."}

@@

The present study aimed to investigate the role of Need for Cognition, the stable preference for and enjoyment of cognitive effort, in the context of burnout in teachers.
To achieve this, we replicated findings of mediators between Need for Cognition and burnout, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
Previous studies have indicated a protective effect of NFC against burnout, but the associations with the burnout subscales were inconsistent, suggesting that there are more variables influencing this relationship.

## Replication of Grass et al. (2018)

@@

```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018)"}

  outlierreplic_table <-
    knitr::kable(outlierreplic_table,
        caption = "Results of the replication of Grass et al. (2018).",
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
    kableExtra::pack_rows("Total Effect", 11, 11) %>%
    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

>>>>

Individuals with high burnout scores are often passive copers, high in neuroticism, low in self-esteem, and have an external locus of control [@Schaufeli2014].
NFC on the other hand is negatively associated with those variables [@Double2016; @Fleischhauer2019; @Ghorbani2004; @Grass2018; @Osberg1987], suggesting that people high in NFC are less prone to experience burnout.
This is supported by findings that NFC showed moderate to large negative associations with burnout scores in adults [@Fleischhauer2019], students [@Fleischhauer2019; @Naderi2018], and student teachers [@Grass2018].
However, the associations of NFC with the sum score and the subscales of the MBI are not always consistent between these studies.
This is likely not caused by inaccurate measurement, since the validity of both NCS [@Bless1994; @Osberg1987; @Tolentino1990] and MBI [@Brady2021; @Kantas1997; @Schaufeli2001; @ValdiviaVazquez2021] has been demonstrated in multiple studies.
What is more likely is the influence of one or more other variables, moderating or mediating the association of NFC and burnout.
Grass et al. [-@Grass2018] investigated such a mediation and found that the relation of NFC and the MBI subscale reduced personal-efficacy was fully mediated by higher habitual use of reappraisal, more active coping, and less passive coping, but not by habitual use of suppression or self-control.
Reappraisal and suppression are two emotion regulation strategies, which refer to the cognitive reassessment of a stressor and the inhibition of emotional reactions, respectively [@Gross1998a].
The findings by Grass et al. [-@Grass2018] suggest that individuals high in NFC experience a weaker decline in personal efficacy in response to long-term stress because they actively reassess the situation in a way that reinforces their sense of self-efficacy and don't avoid dealing with the stressor [@Strobel2017].
One goal of this paper was to replicate the findings of Grass et al. [-@Grass2018] in a teacher sample using a multiple mediation model on cross-sectional self-report data of teachers.
We expected NFC to be negatively associated with reduced personal efficacy via higher reappraisal scores, but not via suppression, via self-control, or directly.

Furthermore, we extended the analysis to other possible mediators.
These mediators were motivated by our own recent survey of the literature on NFC and well-being, which suggested that individuals high in NFC might not only have a high level of personal resources but also overestimate their own resources to a certain degree [@Zerna2021].
This can take the form of patients with higher NFC having lower intentions to consult their physician [@Latimer2007] or adults with higher NFC having higher intentions to consume high calorie beverages [@Gallivan2020] after detailed message interventions designed to promote consultations and healthier beverage choices, respectively.
Only a balance of resources and demands results in personal well-being, while an imbalance threatens well-being, regardless of whether this imbalance is in favour of resources or demands [@Dodge2012].
Following the framework of Hobfoll [-@Hobfoll1989], resources can be objects with practical or status purpose, conditions like marriage or tenure, personality aspects like coping style, and energies such as time, money, or knowledge.
In the case of NFC, resources are from the categories personality and energies: Personality, because NFC is a trait, encompassing a curious, analytic, and passionate approach to challenges, and energies, because individuals high in NFC have been coping actively all their life, which enriches their level of experience and knowledge in approaching challenges [@Cacioppo1996].
These personal resources matter with regard to stress assessment (how the situation is appraised) and with regard to both coping and recovery [@Salanova2006].
We therefore investigated whether the association of NFC and burnout was mediated by different ratios of demands and resources; demands that are too high to be dealt with using one’s personal resources (*demands too high*), demands that are too low for one’s personal resources (*demands too low*), and a balanced fit of demands and resources (*demand-resource-fit*).
Using the same data as for the replication, we computed a structural equation model (SEM) to assess the influence of these mediators.
Since individuals high in NFC are confident in their abilities [@Bye2009; @Ghorbani2004; @Heppner1983; @Klaczynski1996], we expected NFC to be negatively associated with *demands too high*, and positively associated with *demands too low* and *demand-resource-fit*.
And since burnout results from constant unpleasant activation by high demands, we expected it to be positively associated with *demands too high* and negatively associated with *demand-resource-fit*.
However, we had no hypothesis regarding the association of *demands too low* and burnout, because even though *demands too low* is akin to the concept of boredom and the consequences of boredom and burnout are very similar, burnout is a state with even lower activation and even more negative affect than boredom [@Schaufeli2014].
It has already been shown that the Covid-19 pandemic has exacerbated the rising prevalence of burnout [@Froebe2021], so we incorporated the degree of feeling burdened by the pandemic in an exploratory approach.
To sum up, this study had three aims: Replicating findings of mediation between NFC and burnout in a teacher sample, investigating the impact of different demand-resource-ratios on the relationship between NFC and burnout, and exploring the impact of other variables such as perceived burden by the Covid-19 pandemic.

@@

### Replication of Grass et al. (2018) in a teacher sample
Items were reverse coded according to the scale manuals.
NFC and self-control were computed as the sum scores of the NCS and the SCS, respectively.
*Reduced personal efficacy* was computed using the sum of the MBI subscale, and reappraisal and suppression were computed using the sum of each ERQ subscale.
NFC was entered as the independent variable, having a direct and multiple indirect effects on MBI via self-control, reappraisal, and suppression as mediators.
Following Grass et al. [-@Grass2018], bootstrapped confidence intervals with $N=2,000$ replicates <!-- add seed and RNG (likely "Mersenne-Twister" --> were computed to account for deviations from normality.
Multiple indices were used to evaluate model fit as recommended by Hu and Bentler [-@Hu1999]: the Chi-square test statistic, which measures the fit compared to a saturated model (small values indicate better fit of predicted and observed covariances), the Comparative Fit Index (CFI), which compares the fit to the baseline model ($CFI>.95$ indicates good fit, but $CFI>.90$ is also commonly used), the Standardized Root Mean Square Residual (SRMR), which compares the residuals of the observed and predicted covariance matrix ($SRMR<.08$ indicates fair fit, $SRMR<.05$ good fit), and the Root Mean Square Error of Approximation (RMSEA), which does the same as the latter but takes degrees of freedom and model complexity into account ($RMSEA<.08$ indicates acceptable fit, $RMSEA<.05$ good fit, $RMSEA<.01$ excellent fit).

@@

```{r objective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018) in a teacher sample"}

  replic_table <-
    knitr::kable(replic_table,
        caption = "Results of the replication of Grass et al. (2018) in a teacher sample.",
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
    kableExtra::pack_rows("Total Effect", 11, 11) %>%
    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, \\beta = standardized regression coefficient, $CI$ = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote

@@

## Replication of Grass et al. (2018) in a teacher sample

@@

```{r objective1plot, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap="Standardized regression coefficients in the replication of Grass et al. (2018) in a teacher sample. * $p<.05$, ** $p<.01$."}

@@

The present study aimed to investigate the role of Need for Cognition, the stable preference for and enjoyment of cognitive effort, in the context of burnout in teachers.
To achieve this, we replicated findings of mediators between Need for Cognition and burnout in a teacher sample, and extended the analysis to the role of different ratios of demands and resources in burnout using latent variable models.
In an exploratory approach, we investigated the influence of the burden that the Covid-19 pandemic has placed on teachers.
Previous studies have indicated a protective effect of NFC against burnout, but the associations with the burnout subscales were inconsistent, suggesting that there are more variables influencing this relationship.

## Replication of Grass et al. (2018) in a teacher sample

@@

```{r outlierobjective1table, echo=FALSE, message=FALSE, warning=FALSE, caption="Results of the replication of Grass et al. (2018) in a teacher sample"}

  outlierreplic_table <-
    knitr::kable(outlierreplic_table,
        caption = "Results of the replication of Grass et al. (2018) in a teacher sample.",
        booktabs = T, # no vertical lines
        escape = F, # correctly print special characters)
        align = c("l",rep("r",7))) %>% # right aligns the text in every numerical column
    kableExtra::kable_styling(latex_options = c("striped", "scale_down")) %>%
    kableExtra::pack_rows("Direct Effects", 1, 7) %>% # group the rows and add a header in between
    kableExtra::pack_rows("Indirect Effects", 8, 10) %>%
    kableExtra::pack_rows("Total Effect", 11, 11) %>%
    kableExtra::footnote(general = "$B$ = unstandardized regression coefficient, $\\beta$ = standardized regression coefficient, CI = confidence interval, NFC = Need for Cognition, RPE = reduced personal efficacy subscale of the Maslach Burnout Inventory, $SE$ = standard error, $N=179$.",
             escape = F, # correctly print special characters
             threeparttable = T)# line breaks in the footnote
